Pursuit of Happiness: The impact of growing Western criticism on Chinese Wellbeing\thanks{Code and data are available at: https://github.com/alexandersunliang/china\_wellbeing2bugfix.git}

### 2024-04-23 paper/paper.tex
i can't fix it i give up

---
title: "Pursuit of Happiness: The impact of growing Western criticism on Chinese Wellbeing"
author: 
  - Alexander Sun
thanks: "Code and data are available at: https://github.com/alexandersunliang/china_wellbeing2bugfix.git"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(arrow)
library(here)
library(modelsummary)
library(knitr)
library(kableExtra)
wvsdata <- read_parquet(here("data/analysis_data/analysis_data2018.parquet"))
```

# Introduction {#sec-intro}

Since the early 1990s, China's economy has grown significantly, with an average annual GDP growth rate of around 10%. The 1990s market reforms aimed to control capitalism, showing that socialism could harness capitalist growth to increase national power. Today, China is a global economic leader, second only to the US in GDP; however, it is essential to assess how these changes affect societal well-being. Studies present mixed views on the effects of socialism and democracy. Cheung and Leung (2007) found that collectivism significantly impacts the well-being of the Chinese, whereas Hofstede (1980) observed that individualism encourages economic growth. Moore (2005) argued that the freedoms introduced in the 1980s led the Chinese towards a strong form of individualism, which starkly contrasts with the collectivist approach of the Cultural Revolution. Steele and Lynch examined whether individualist or collectivist traits prevail in modern China and their impact on subjective well-being (SWB). They focused on how these orientations predict SWB and if their influence has shifted as China transitioned towards a market economy.

While Steele and Lynch researched the impacts of the reform, this paper will attempt to reframe their ideas with a focus on the impacts of COVID-19. This study will replicate and extend Steele and Lynch’s previous research by examining the prevailing sentiments—individualist versus collectivist—in China post-COVID-19 in 2022 and their implications for SWB. We analyze whether and how the relationship between these cultural orientations and well-being has evolved in the context of China's continued economic and social transformations.

@@

The remainder of the paper is structured as follows: following in the introduction in [@sec-intro], [@sec-data] provides an overview of our dataset, variables, and a quick analysis of the data, [@sec-model] discusses the model we chose for our regression, [@sec-results] depicts the calculated values along with any important measurements, and [@sec-discussion] discusses the implications of our results while also suggesting avenues for future research.

# Data {#sec-data}

## Data Source and Measurement

@@

## Variables

@@

 - **Happiness**: Our dependent variable was measured as "life satisfaction" in the questionnaire. Participants responded with how happy they were with their current lifestyle on a scale of 1-10 with 1 being "completely dissatisfied" and 10 being "completely satisfied". We will later conduct a model to estimate this value based off our other regressors.

 - **National Pride**: Respondents were asked about their national pride with the question, "How proud are you to be Chinese?" We believe that this is especially important as it allows us to see temporal trends in nationalism with regards to increasing Western criticism.

 - **Government Surveillance in Public Areas**: This question asks if participants believe that the government has the right to surveil the populace in public areas. As this is one of the largest criticisms against the modern Chinese government, we can potentially see impacts of this variable with respect to life satisfaction for citizens. This variable is recorded on a scale of 1-4, with one being "Definitely should not have the right" and four being "Definitely should have the right"

 - **The Right for the Government to Monitor Emails**: This variable measures population sentiment for the governments ability to monitor private emails. While the last variable evaluated opinions on surveillance in public areas, this one angles more towards public sentiment on the collection of private information. This was also recorded on a scale of 1-4, with one being "Definitely should not have the right" and four being "Definitely should have the right".

 - **Should the Government Take More Responsibility to Ensure Everyone is Provided For?**: As the divide between communist and democratic ideals grow, this question will provide insight into the collectivist support among the general public in China. Although not a perfect capture of sentiment towards communism, this is the closest question that was able to be asked on the survey without running into political issues. This was recorded on a scale of 1-10, with one being the respondent completely agrees with the question and ten being the respondent completely disagrees.

 - **Age**: With the onset of social media, especially TikTok/Douyin, Chinese citizens are being exposed to more Western media than ever before. By measuring age, we can see if specific generations are more progressive than others. The World Values Survey limits the age of its participants to between 18 and 70.

## Data Analysis

Our investigation was conducted using the programming language R [@citeR], with the packages [@tidyverse], and [@dplyr]

Although each of the variables have a different scale, the summary statistics of the current dataset can be seen in @fig-summary

```{r}
#| echo: false
#| label: fig-summary
#| fig-cap: Summary Statistics for World Values Survey
library(knitr)
library(kableExtra)
library(dplyr)
library(tidyr)

variables_of_interest <- c("National_Pride", "Happiness", "Government_Surveillance", 
                           "Email_Monitoring", "Information_Collection", 
                           "Government_Responsibility", "age")

summary_stats <- wvsdata %>%
  summarise(across(all_of(variables_of_interest), list(
    Mean = ~round(mean(.x, na.rm = TRUE), 2),
    SD = ~round(sd(.x, na.rm = TRUE), 2),
    Median = ~median(.x, na.rm = TRUE),
    Q1 = ~quantile(.x, probs = 0.25, na.rm = TRUE),
    Q3 = ~quantile(.x, probs = 0.75, na.rm = TRUE),
    Min = ~min(.x, na.rm = TRUE),
    Max = ~max(.x, na.rm = TRUE)
  ), .names = "{.col}_{.fn}"))

summary_stats_long <- summary_stats %>%
  pivot_longer(cols = everything(), names_to = c("Variable", "Statistic"), names_pattern = "(.+)_(Mean|SD|Median|Q1|Q3|Min|Max)")

summary_stats_wide <- summary_stats_long %>%
  pivot_wider(names_from = Statistic, values_from = value)

summary_table <- kable(summary_stats_wide, format = "latex", booktabs = TRUE, 
                       caption = "Descriptive Statistics for Selected Variables") %>%
  row_spec(0, bold = TRUE)

summary_table
```

@@

We can also see the distribution for each of our variables in @fig-distgraphs:

```{r}
#| echo: false
#| label: fig-distgraphs
#| fig-cap: Assorted Variable Distributions
#| warning: false
#| fig.height: 7

library(ggplot2)
library(gridExtra)

# Create a list to hold the ggplot objects
plot_list <- list()

plot_list[['National Pride']] <- ggplot(wvsdata, aes(x = National_Pride)) + 
      geom_histogram(bins = 5, fill = "blue") + 
      labs(title = "National Pride", x = "Responses (1-5)", y = "Count")

plot_list[['Happiness']] <- ggplot(wvsdata, aes(x = Happiness)) + 
      geom_histogram(bins = 10, fill = "red") + 
      labs(title = "Happiness", x = "Responses (1-10)", y = "Count")

plot_list[['Government Surveillance']] <- ggplot(wvsdata, aes(x = Government_Surveillance)) + 
      geom_histogram(bins = 4, fill = "green") + 
      labs(title = "Surveillance Support", x = "Responses (1-4)", y = "Count")

plot_list[['Email Monitoring']] <- ggplot(wvsdata, aes(x = Email_Monitoring)) + 
      geom_histogram(bins = 4, fill = "orange") + 
      labs(title = "Email Monitoring", x = "Responses (1-4)", y = "Count")

plot_list[['Information Collection']] <- ggplot(wvsdata, aes(x = Information_Collection)) + 
      geom_histogram(bins = 4, fill = "purple") + 
      labs(title = "Information Collection", x = "Responses (1-4)", y = "Count")

plot_list[['Government Responsibility']] <- ggplot(wvsdata, aes(x = Government_Responsibility)) + 
      geom_histogram(bins = 4, fill = "brown") + 
      labs(title = "Government Responsibility", x = "Responses (1-10)", y = "Count")

plot_list[['Age']] <- ggplot(wvsdata, aes(x = age)) + 
      geom_histogram(bins = 52, fill = "cyan") + 
      labs(title = "Age", x = "Age", y = "Count")

# Arrange the plots into a grid with 2 columns
do.call(grid.arrange, c(plot_list, ncol = 2))

```

From the distribution graphs shown in @fig-distgraphs, we observe that barely any of the questions are normally distributed as we would expect for such a large sample. Although this could be attributed to the limited range of answers, we notice that even for questions with a larger range of responses like happiness and government responsibility, the data seems very skewed to one side.

Furthermore, the dataset provides information on how responses to question differ based off age. From this, we can depict how different age groups tend to respond to questions. For example, we expect the younger generation to be more progressive, leading to higher disapproval rates for government surveillance policies. Information on age distributions on support for government surveillance is shown in @fig-govsurvsup.
```{r}
#| echo: false
#| warning: false
#| fig-cap: "Support for Government Surveillance Between Ages"
#| label: fig-govsurvsup
wvsdata <- wvsdata %>%
  mutate(Age_Group = cut(age, 
                         breaks = c(18, 25, 35, 45, 55, 65, Inf),
                         labels = c("18-25", "26-35", "36-45", "46-55", "56-65", "66+"),
                         include.lowest = TRUE))
ggplot(wvsdata, aes(x = Age_Group, fill = as.factor(Government_Surveillance))) +
  geom_bar(position = "dodge") +
  labs(title = "Government Surveillance Support by Age Group",
       x = "Age Group",
       y = "Count",
       fill = "Gov. Surveillance\nSupport Level") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Surprisingly, we see that as age increases, a higher proportion of adults in that age group are opposed to government surveillance in public areas. As the question asks about government surveillance in public areas, we can potentially infer citizens may oppose government email/information supervision as those are more private. However, as seen in @fig-compiled, we notice that the support for the collection of information for anybody in China is significantly higher than the other variables.

# Model {@sec-model}

The potential of using the World Values Survey data to predict happiness is based on the idea that certain key variables, such as attitudes towards governance and societal structures, are able to predict an individual’s level of happiness. Our model will hopefully be able to show how and if specific perceptions on government surveillance acceptance, email monitoring, and information collection are indicative of broader societal satisfaction.

Before we develop our model, we have to assume that there is a relationship between our variables and happiness level. Research consistently indicates that the trust in, and perception of, governmental and societal systems significantly influences personal well-being (Helliwell & Putnam, 2004). We postulate that individuals’ responses to questions about governance and privacy are not merely reflective of their current state but are shaped by their broader socio-political environment and personal experiences. Therefore, a person's level of happiness is not only a function of their immediate circumstances but also a reflection of their interactions with the societal and political structures they inhabit (Bjørnskov, 2006).

@@

Furthermore, cultural factors could moderate the relationship between governance attitudes and happiness. For example, in societies where collective well-being is emphasized, the acceptance of surveillance measures might correlate differently with happiness compared to societies that prioritize individual autonomy (Oishi, Diener, & Lucas, 2007). We expect that the effects for the government policies and age to be positive, while national pride is negative.

## Model set-up

Define $y_i$ as the estimated level of happiness. Then $\beta_0$ would be the estimated level of happiness given that all other variables are zero, $\beta_i$ would be the respective effects on estimated levels of happiness for each of our variables. The full model form is shown below:

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

## Model justification

@@

Our large sample size—approximately 3000 respondents—strengthens the model further. A robust sample size ensures that our parameter estimates are reliable and reduces the likelihood of statistical errors. It also increases the generalizability of our findings, ensuring that our conclusions are not just applicable to a narrow subset of the population but can be extended to China as a whole. Additionally, a larger dataset supports the complexity of our model, allowing us to include multiple predictors without the risk of overfitting, thereby maintaining the model’s integrity and robustness. The overall statistical significance of our test will be examined further later in this study.

# Results {@sec-results}

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

happiness_model <- readRDS(here(file = "models/happiness_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Regression Model Results for Predicting Happiness Based on Government Perceptions and Age"
#| warning: false

library(modelsummary)
modelsummary::modelsummary(
  happiness_model,
  statistic = "mad",  
  fmt = 2  
)
```
The regression analysis presented in @tbl-modelresults reveals an expected baseline happiness level of 7.60, as indicated by the model's intercept. This suggests a generally positive baseline level of happiness among respondents when all other variables are held constant. The coefficients for the support for government surveillance, email monitoring, and information collection are slightly negative, at -0.06, -0.01, and -0.01 respectively, suggesting a marginal decrease in happiness scores associated with increased acceptance of these governance measures. Notably, national pride shows a stronger negative association with happiness, with a coefficient of -0.50, indicating a significant decrease in happiness as national pride increases. In contrast, the age coefficient of 0.02 suggests a slight increase in happiness with age.

The model accounts for a modest 4.8% of the variance in happiness scores, as reflected by an R-squared value of 0.048, implying that other unexamined factors may play a more substantial role in influencing happiness. The adjusted R-squared value, at 0.043, indicates a minimal increase in explanatory power when accounting for the number of predictors. Furthermore, the Root Mean Square Error (RMSE) of 1.98 points to the model's prediction errors' standard deviation, signifying potential areas for model refinement. These results provide a statistical basis for the model's performance, emphasizing the nuanced challenge of predicting subjective well-being through perceived governance and age.
```{r}
#| echo: false
#| eval: true
#| warning: false
#| label: fig-checks
#| fig-cap: "Happiness Model Checks"
library(rstanarm)
library(bayesplot)
library(ggplot2)

ppc_dens_overlay(y = wvsdata$Happiness, yrep = posterior_predict(happiness_model))

mcmc_trace(
  as.array(happiness_model),
  pars = c("(Intercept)", "Government_Surveillance", "Email_Monitoring", "Information_Collection", "National_Pride", "age", "Government_Responsibility")
)
```
The posterior predictive check, visualized by @fig-checks, helps us evaluate the fit of our Bayesian model. By overlapping the observed happiness data with the simulated posterior predictive values, this plot illustrates how well our model reproduces the observed outcomes. The congruence between the values signifies that the model adequately captures the central tendency and variability of the actual happiness scores. Notably, if there are significant deviations it could indicate that the model may not fully account for the data's characteristics, prompting us to consider model refinements or additional predictors.

The trace plot provides a representation of the Markov Chain Monte Carlo (MCMC) sampling process, essential for evaluating the convergence of the chains. Each parameter's trace, represented by individual lines for each chain, should display a "mixing" behavior, converging to and fluctuating around a common value, without exhibiting trends or periodicity. Such patterns indicate that the chains have reached a stationary distribution, and the samples drawn are likely from the true posterior distribution. If the chains do not converge, this implies that the sampling process has not yet adequately captured the full behaviour of the true distribution, and further iterations or model adjustments may be required to ensure reliable inference.

# Discussion {@sec-discussion}

## Model Findings {#sec-first-point}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\usepackage{siunitx}

  \newcolumntype{d}{S[
    input-open-uncertainty=,
    input-close-uncertainty=,
    parse-numbers = false,
    table-align-text-pre=false,
    table-align-text-post=false
  ]}

\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Pursuit of Happiness: The impact of growing Western criticism on Chinese Wellbeing},
  pdfauthor={Alexander Sun},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{Pursuit of Happiness: The impact of growing Western criticism on
Chinese Wellbeing\thanks{Code and data are available at:
https://github.com/alexandersunliang/china\_wellbeing2bugfix.git}}
\author{Alexander Sun}
\date{April 22, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, enhanced, interior hidden, boxrule=0pt, breakable]}{\end{tcolorbox}}\fi

\renewcommand*\contentsname{Table of contents}
{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{3}
\tableofcontents
}
\hypertarget{sec-intro}{%
\section{Introduction}\label{sec-intro}}

Since the early 1990s, China's economy has grown significantly, with an
average annual GDP growth rate of around 10\%. The 1990s market reforms
aimed to control capitalism, showing that socialism could harness
capitalist growth to increase national power. Today, China is a global
economic leader, second only to the US in GDP; however, it is essential
to assess how these changes affect societal well-being. Studies present
mixed views on the effects of socialism and democracy. Cheung and Leung
(2007) found that collectivism significantly impacts the well-being of
the Chinese, whereas Hofstede (1980) observed that individualism
encourages economic growth. Moore (2005) argued that the freedoms
introduced in the 1980s led the Chinese towards a strong form of
individualism, which starkly contrasts with the collectivist approach of
the Cultural Revolution. Steele and Lynch examined whether individualist
or collectivist traits prevail in modern China and their impact on
subjective well-being (SWB). They focused on how these orientations
predict SWB and if their influence has shifted as China transitioned
towards a market economy.

While Steele and Lynch researched the impacts of the reform, this paper
will attempt to reframe their ideas with a focus on the impacts of
COVID-19. This study will replicate and extend Steele and Lynch's
previous research by examining the prevailing sentiments---individualist
versus collectivist---in China post-COVID-19 in 2022 and their
implications for SWB. We analyze whether and how the relationship
between these cultural orientations and well-being has evolved in the
context of China's continued economic and social transformations.

@@

The remainder of the paper is structured as follows: following in the
introduction in Section~\ref{sec-intro}, Section~\ref{sec-data} provides
an overview of our dataset, variables, and a quick analysis of the data,
\textbf{?@sec-model} discusses the model we chose for our regression,
\textbf{?@sec-results} depicts the calculated values along with any
important measurements, and \textbf{?@sec-discussion} discusses the
implications of our results while also suggesting avenues for future
research.

\hypertarget{sec-data}{%
\section{Data}\label{sec-data}}

\hypertarget{data-source-and-measurement}{%
\subsection{Data Source and
Measurement}\label{data-source-and-measurement}}

@@

\hypertarget{variables}{%
\subsection{Variables}\label{variables}}

@@

\begin{itemize}
\item
  \textbf{Happiness}: Our dependent variable was measured as ``life
  satisfaction'' in the questionnaire. Participants responded with how
  happy they were with their current lifestyle on a scale of 1-10 with 1
  being ``completely dissatisfied'' and 10 being ``completely
  satisfied''. We will later conduct a model to estimate this value
  based off our other regressors.
\item
  \textbf{National Pride}: Respondents were asked about their national
  pride with the question, ``How proud are you to be Chinese?'' We
  believe that this is especially important as it allows us to see
  temporal trends in nationalism with regards to increasing Western
  criticism.
\item
  \textbf{Government Surveillance in Public Areas}: This question asks
  if participants believe that the government has the right to surveil
  the populace in public areas. As this is one of the largest criticisms
  against the modern Chinese government, we can potentially see impacts
  of this variable with respect to life satisfaction for citizens. This
  variable is recorded on a scale of 1-4, with one being ``Definitely
  should not have the right'' and four being ``Definitely should have
  the right''
\item
  \textbf{The Right for the Government to Monitor Emails}: This variable
  measures population sentiment for the governments ability to monitor
  private emails. While the last variable evaluated opinions on
  surveillance in public areas, this one angles more towards public
  sentiment on the collection of private information. This was also
  recorded on a scale of 1-4, with one being ``Definitely should not
  have the right'' and four being ``Definitely should have the right''.
\item
  \textbf{Should the Government Take More Responsibility to Ensure
  Everyone is Provided For?}: As the divide between communist and
  democratic ideals grow, this question will provide insight into the
  collectivist support among the general public in China. Although not a
  perfect capture of sentiment towards communism, this is the closest
  question that was able to be asked on the survey without running into
  political issues. This was recorded on a scale of 1-10, with one being
  the respondent completely agrees with the question and ten being the
  respondent completely disagrees.
\item
  \textbf{Age}: With the onset of social media, especially
  TikTok/Douyin, Chinese citizens are being exposed to more Western
  media than ever before. By measuring age, we can see if specific
  generations are more progressive than others. The World Values Survey
  limits the age of its participants to between 18 and 70.
\end{itemize}

\hypertarget{data-analysis}{%
\subsection{Data Analysis}\label{data-analysis}}

Our investigation was conducted using the programming language R (R Core
Team 2023), with the packages (\textbf{tidyverse?}), and
(\textbf{dplyr?})

Although each of the variables have a different scale, the summary
statistics of the current dataset can be seen in
Figure~\ref{fig-summary}

\begin{figure}

{\centering

\hypertarget{fig-summary-1}{}
\begin{table}

\caption{Descriptive Statistics for Selected Variables}
\centering
\begin{tabular}[t]{lrrrrrrr}
\toprule
\textbf{Variable} & \textbf{Mean} & \textbf{SD} & \textbf{Median} & \textbf{Q1} & \textbf{Q3} & \textbf{Min} & \textbf{Max}\\
\midrule
National\_Pride & 1.64 & 0.64 & 2 & 1 & 2 & 1 & 5\\
Happiness & 7.42 & 2.02 & 8 & 6 & 9 & 1 & 10\\
Government\_Surveillance & 1.82 & 0.89 & 2 & 1 & 2 & 1 & 4\\
Email\_Monitoring & 2.30 & 0.98 & 2 & 2 & 3 & 1 & 4\\
Information\_Collection & 2.48 & 1.04 & 2 & 2 & 3 & 1 & 4\\
\addlinespace
Government\_Responsibility & 5.22 & 2.82 & 5 & 3 & 8 & 1 & 10\\
age & 44.46 & 14.48 & 45 & 32 & 56 & 18 & 70\\
\bottomrule
\end{tabular}
\end{table}

}

\caption{\label{fig-summary}Summary Statistics for World Values Survey}

\end{figure}

@@

We can also see the distribution for each of our variables in
Figure~\ref{fig-distgraphs}:

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-distgraphs-1.pdf}

}

\caption{\label{fig-distgraphs}Assorted Variable Distributions}

\end{figure}

From the distribution graphs shown in Figure~\ref{fig-distgraphs}, we
observe that barely any of the questions are normally distributed as we
would expect for such a large sample. Although this could be attributed
to the limited range of answers, we notice that even for questions with
a larger range of responses like happiness and government
responsibility, the data seems very skewed to one side.

Furthermore, the dataset provides information on how responses to
question differ based off age. From this, we can depict how different
age groups tend to respond to questions. For example, we expect the
younger generation to be more progressive, leading to higher disapproval
rates for government surveillance policies. Information on age
distributions on support for government surveillance is shown in
Figure~\ref{fig-govsurvsup}.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-govsurvsup-1.pdf}

}

\caption{\label{fig-govsurvsup}Support for Government Surveillance
Between Ages}

\end{figure}

Surprisingly, we see that as age increases, a higher proportion of
adults in that age group are opposed to government surveillance in
public areas. As the question asks about government surveillance in
public areas, we can potentially infer citizens may oppose government
email/information supervision as those are more private. However, as
seen in Figure~\ref{fig-compiled}, we notice that the support for the
collection of information for anybody in China is significantly higher
than the other variables.

\hypertarget{model-sec-model}{%
\section{\texorpdfstring{Model
\{\textbf{?@sec-model}\}}{Model \{?@sec-model\}}}\label{model-sec-model}}

The potential of using the World Values Survey data to predict happiness
is based on the idea that certain key variables, such as attitudes
towards governance and societal structures, are able to predict an
individual's level of happiness. Our model will hopefully be able to
show how and if specific perceptions on government surveillance
acceptance, email monitoring, and information collection are indicative
of broader societal satisfaction.

Before we develop our model, we have to assume that there is a
relationship between our variables and happiness level. Research
consistently indicates that the trust in, and perception of,
governmental and societal systems significantly influences personal
well-being (Helliwell \& Putnam, 2004). We postulate that individuals'
responses to questions about governance and privacy are not merely
reflective of their current state but are shaped by their broader
socio-political environment and personal experiences. Therefore, a
person's level of happiness is not only a function of their immediate
circumstances but also a reflection of their interactions with the
societal and political structures they inhabit (Bjørnskov, 2006).

@@

Furthermore, cultural factors could moderate the relationship between
governance attitudes and happiness. For example, in societies where
collective well-being is emphasized, the acceptance of surveillance
measures might correlate differently with happiness compared to
societies that prioritize individual autonomy (Oishi, Diener, \& Lucas,
2007). We expect that the effects for the government policies and age to
be positive, while national pride is negative.

\hypertarget{model-set-up}{%
\subsection{Model set-up}\label{model-set-up}}

Define \(y_i\) as the estimated level of happiness. Then \(\beta_0\)
would be the estimated level of happiness given that all other variables
are zero, \(\beta_i\) would be the respective effects on estimated
levels of happiness for each of our variables. The full model form is
shown below:

@@

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}.

\hypertarget{model-justification}{%
\subsection{Model justification}\label{model-justification}}

@@

Our large sample size---approximately 3000 respondents---strengthens the
model further. A robust sample size ensures that our parameter estimates
are reliable and reduces the likelihood of statistical errors. It also
increases the generalizability of our findings, ensuring that our
conclusions are not just applicable to a narrow subset of the population
but can be extended to China as a whole. Additionally, a larger dataset
supports the complexity of our model, allowing us to include multiple
predictors without the risk of overfitting, thereby maintaining the
model's integrity and robustness. The overall statistical significance
of our test will be examined further later in this study.

\hypertarget{results-sec-results}{%
\section{\texorpdfstring{Results
\{\textbf{?@sec-results}\}}{Results \{?@sec-results\}}}\label{results-sec-results}}

Our results are summarized in Table~\ref{tbl-modelresults}.

\hypertarget{tbl-modelresults}{}
\begin{table}
\caption{\label{tbl-modelresults}Regression Model Results for Predicting Happiness Based on Government
Perceptions and Age }\tabularnewline

\centering
\begin{tabular}[t]{lc}
\toprule
  & (1)\\
\midrule
(Intercept) & \num{7.23}\\
 & (\num{0.21})\\
Government\_Surveillance & \num{-0.06}\\
 & \vphantom{1} (\num{0.05})\\
Email\_Monitoring & \num{0.00}\\
 & (\num{0.05})\\
Information\_Collection & \num{-0.01}\\
 & (\num{0.04})\\
National\_Pride & \num{-0.50}\\
 & (\num{0.06})\\
age & \num{0.02}\\
 & (\num{0.00})\\
Government\_Responsibility & \num{0.05}\\
 & (\num{0.01})\\
\midrule
Num.Obs. & \num{2950}\\
R2 & \num{0.054}\\
R2 Adj. & \num{0.048}\\
Log.Lik. & \num{-6186.433}\\
ELPD & \num{-6193.8}\\
ELPD s.e. & \num{44.4}\\
LOOIC & \num{12387.7}\\
LOOIC s.e. & \num{88.8}\\
WAIC & \num{12387.7}\\
RMSE & \num{1.97}\\
\bottomrule
\end{tabular}
\end{table}

The regression analysis presented in Table~\ref{tbl-modelresults}
reveals an expected baseline happiness level of 7.60, as indicated by
the model's intercept. This suggests a generally positive baseline level
of happiness among respondents when all other variables are held
constant. The coefficients for the support for government surveillance,
email monitoring, and information collection are slightly negative, at
-0.06, -0.01, and -0.01 respectively, suggesting a marginal decrease in
happiness scores associated with increased acceptance of these
governance measures. Notably, national pride shows a stronger negative
association with happiness, with a coefficient of -0.50, indicating a
significant decrease in happiness as national pride increases. In
contrast, the age coefficient of 0.02 suggests a slight increase in
happiness with age.

The model accounts for a modest 4.8\% of the variance in happiness
scores, as reflected by an R-squared value of 0.048, implying that other
unexamined factors may play a more substantial role in influencing
happiness. The adjusted R-squared value, at 0.043, indicates a minimal
increase in explanatory power when accounting for the number of
predictors. Furthermore, the Root Mean Square Error (RMSE) of 1.98
points to the model's prediction errors' standard deviation, signifying
potential areas for model refinement. These results provide a
statistical basis for the model's performance, emphasizing the nuanced
challenge of predicting subjective well-being through perceived
governance and age.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-checks-1.pdf}

}

\caption{\label{fig-checks-1}Happiness Model Checks}

\end{figure}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-checks-2.pdf}

}

\caption{\label{fig-checks-2}Happiness Model Checks}

\end{figure}
